Awareness and Russellian Epistemology

### 2011-01-30 completeness2.tex
Reworked completeness

  This model makes true the following properties:
  \begin{enumerateroman}
    \item $\sim_{\forall}$ is an equivalence relation    
    \item $R_{\Box} \subseteq \sim_{\forall}$
    \item In each equivalence class specified by $\sim_{\forall}$, there is at
    most one world making true $i$ for all $i \in \Upsilon$
  \end{enumerateroman}
  As in our previous construction we have that there is some world $w$ where
  $\mathbbm{M}, w \nvDash \psi$.  Let $\mathbbm{M}' = \langle W', V',
  R_{\Box}', \sim_{\forall}', \mathcal{A}' \rangle$ be the submodel generated
  by $\{w\}$; we have that $\mathbbm{M}', w \nvDash \psi$ (see {\cite[chapter
  2.1]{blackburn_modal_2001}} for details on generated submodels).  In this
  model $\forall$ is a universal modality and either $\left\llbracket i
  \right\rrbracket^{\mathbbm{M}'} = \varnothing$ or $\left\llbracket i
  \right\rrbracket^{\mathbbm{M}'} =\{v\}${\footnote{As per the usual
  convention, here $\left\llbracket \phi \right\rrbracket^{\mathbbm{M}}$
  denotes $\{w \in W \  | \  \mathbbm{M}, w \vDash
  \phi\}$.  We will drop $\mathbbm{M}$ where it is unambiguous.}}. Since the
  store $\Psi$ of nominals is infinite and $\Upsilon$ is finite, we have that
  $\Psi \backslash \Upsilon$ is infinite, so there is some injection $\iota :
  W' \hookrightarrow \Psi \backslash \Upsilon$ which assigns a fresh nominal
  to every world.  Let $\mathbbm{M}'' = \langle W'', V'', R'', \mathcal{A}'',
  \ell \rangle$, where:
  \begin{center}
    \begin{tabular}{lllll}
      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign V' (p)$\\
      $\bullet$ & $R'' \assign R'_{\Box}$ & \ \  & $\bullet$ &
      $\mathcal{A}'' (v) \assign \{\phi \  | \  \phi \in
      \mathcal{A}' (v)\} \cup \{\neg \iota (u) \  | \ 
      \neg v R' u\}$\\
       $\bullet$ & \begin{tabular}{ll}
       $\ell (i) \assign \left\{ \begin{array}{ll}
          w & i \in \Upsilon \  \& \  \mathbbm{M}, w
          \vDash i\\
          \iota^{- 1} (i) & i \in \iota [W]\\
          \text{undefined} & \text{o/w}
        \end{array} \right.$
      \end{tabular} &  & $\bullet$ &  $R'' \assign R'_{\Box}$ 
    \end{tabular}
  \end{center}

  The the worlds is $\mathbbm{M}'$ and $\mathbbm{M}''$ agree on all
  subformulae of $\psi$, hence $\mathbbm{M}'', w \nvDash
  \psi$. Moreover, the logic in Table \ref{logic2} itself 
  is suitable for $\mathbbm{M}''$ and
  $\mathbbm{M}''$ makes true $\textup{\tmtextbf{CSQ}}_{\vdash}$.  From
  this it follows that we have completeness.
\end{proof}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

>>>>

  This model makes true the following properties:
  \begin{enumerateroman}
    \item \label{hybprop1} $\sim_{\forall}$ is an equivalence relation
    \item If $\mathbbm{M}, v \vDash A : \psi$ then $\mathbbm{M}, v
      \vDash \Box \psi$     
    \item $R_{\Box} \subseteq \sim_{\forall}$
    \item \label{hybprop4}In each equivalence class specified by $\sim_{\forall}$, there is at
    most one world making true $i$ for all $i \in \Upsilon$
  \end{enumerateroman}
  As in our previous construction we have that there is some world $w$ where
  $\mathbbm{M}, w \nvDash \psi$.  Let $\mathbbm{M}' = \langle W', V',
  R_{\Box}', \sim_{\forall}', \mathcal{A}' \rangle$ be the submodel generated
  by $\{w\}$; we have that $\mathbbm{M}', w \nvDash \psi$ (see {\cite[chapter
  2.1]{blackburn_modal_2001}} for details on generated submodels).  In this
  model $\forall$ is a universal modality and either $\left\llbracket i
  \right\rrbracket^{\mathbbm{M}'} = \varnothing$ or $\left\llbracket i
  \right\rrbracket^{\mathbbm{M}'} =\{v\}${\footnote{As per the usual
  convention, here $\left\llbracket \phi \right\rrbracket^{\mathbbm{M}}$
  denotes $\{w \in W \  | \  \mathbbm{M}, w \vDash
  \phi\}$.  We will drop $\mathbbm{M}$ where it is unambiguous.}}. Since the
  store $\Psi$ of nominals is infinite and $\Upsilon$ is finite, we have that
  $\Psi \backslash \Upsilon$ is infinite, so there is some injection $\iota :
  W' \hookrightarrow \Psi \backslash \Upsilon$ which assigns a fresh nominal
  to every world.  Let $\mathbbm{M}'' = \langle W'', V'', R'', \mathcal{A}'',
  \ell \rangle$, where:
  \begin{center}
    \begin{tabular}{lllll}
      $\bullet$ & $W'' \assign W'$ &  & $\bullet$ & $V'' (p) \assign V' (p)$\\
      $\bullet$ & $R'' \assign R'_{\Box}$ & \ \  & $\bullet$ &
      $\mathcal{A}'' (v) \assign \{\phi \  | \  \phi \in
      \mathcal{A}' (v)\} \cup \{\neg \iota (u) \  | \ 
      \neg v R' u\}$\\
       $\bullet$ & \begin{tabular}{ll}
       $\ell (i) \assign \left\{ \begin{array}{ll}
          w & i \in \Upsilon \  \& \  \mathbbm{M}, w
          \vDash i\\
          \iota^{- 1} (i) & i \in \iota [W]\\
          \text{undefined} & \text{o/w}
        \end{array} \right.$
      \end{tabular} &  & $\bullet$ &  $R'' \assign R'_{\Box}$ 
    \end{tabular}
  \end{center}

  The the worlds is $\mathbbm{M}'$ and $\mathbbm{M}''$ agree on all  subformulae of $\psi$, hence $\mathbbm{M}'', w \nvDash
  \psi$. Note that both $\mathbb{M}'$ and $\mathbb{M}''$ inherit
  properties \ref{hybprop1} through \ref{hybprop4} from $\mathbb{M}$.
  This implies that the logic in Table \ref{logic2} itself 
  is suitable for $\mathbbm{M}''$. Moreover, one can show that
  $\mathbbm{M}''$ makes true $\textup{\tmtextbf{CSQ}}_{\vdash}$, using
  a line of argument analogous to what we have provided in previous proofs.
  From this we have enough to establish completeness.
\end{proof}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End:
